\chapter{Theory}

\section{Differential Drive Robotics}
Write something like this:
Differential drive robots is a certain type of wheeled robot that navigate by turning the wheels on each side of its body at different rates.

\section{Inertial Measurement Unit}


\section{LiDAR}
Light Detection and Ranging sensors, are sensors that utilise light and time-of-flight principle to determine the distance from a sensor to an obstacle. 

\section{Localisation and Mapping}
This section describes different localisation and mapping methodologies, specifically Simultaneous Localisation And Mapping(SLAM) and Adaptive Monte Carlo Localisation(AMCL). SLAM is a localisation and mapping method that simultaneously generates a map of it's environment as it does the localisation. AMCL is a particle-based localisation algorithm that is often used in robotics to determine the location of a robot in it's environment.

\section{Robotic Manipulation}
Moveit 2 is an open-source robot manipulator planning and manipulation framework based on ROS 2. It provides tools like anti-collision and gives robotic manipulators using  ROS 2 a robust platform for manipulation. Integration with ROS 2 means that this framework is widely used within the robotics community

\section{Tag Based 3D Machine Vision}
AprilTags are a system of visual tags developed by researchers at the University of Michigan to provide low overhead, high accuracy localisation for many different applications. 

\section{Robot Operating System 2}
Robot operating system 2 is an open source operating system for robots that is aimed at simplifying the communication between different sensors and actuators in a robotic system, and present the information from these different sensors and actuators in a standardised matter.

\subsection{URDF}


\subsection{Navigation 2}
Navigation 2(NAV 2) is a open-source navigation stack based on ROS 2. It's modular design is made to provide a robust navigation platform for robots utilising ROS 2.
